---
---
title: "Week 6 Summary"
output: html_notebook
---
Add surrogate key to flights.

```{r}
library(dplyr)
library(purrr)
library(tidyverse)
library(nycflights13)

flights %>% 
  count(year, month, day, flight) %>% 
  filter(n > 1)

##we see that date, plus flight number is not an unique identifier
```
```{r}
flights %>% 
  mutate(flight_id = row_number()) %>%
  glimpse()


```
Identify the keys in the following datasets

Lahman::Batting,
```{r}
library('Lahman')
Lahman::Batting %>%
  count(playerID, yearID, stint) %>%
  filter(n > 1) %>%
  nrow()
```

babynames::babynames

```{r}
library('babynames')
babynames::babynames %>%
  glimpse() %>%
  print()
##key would be name per year per sex
babynames::babynames %>%
  count(year, name, sex) %>%
  filter(n > 1) %>%
  nrow()
##output is [1] 0


```

nasaweather::atmos

```{r}
library(nasaweather)
nasaweather::atmos %>%
  glimpse() %>%
  print()
##looking at the dataset
nasaweather::atmos %>%
  count(lat, long, year, month)%>%
    filter(n>1) %>%
    nrow()
  ##output is 0
  
```

fueleconomy::vehicles

```{r}
library(fueleconomy)
fueleconomy::vehicles %>%
  glimpse()%>%
  print()
##seeing the columns present

fueleconomy::vehicles %>%
  count(id)%>%
  filter(n>1)%>%
  nrow()
##output is 0
  
```
Pivoting
```{r}
library(tidyverse)
table4a
##need year column but instead have distinct years
table4a %>% 
  pivot_longer(c(`1999`, `2000`), names_to = "year", values_to = "cases")
```
```{r}
##Why are pivot_longer() and pivot_wider() not perfectly symmetrical?
##Carefully consider the following example:

stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks %>% 
  pivot_wider(names_from = year, values_from = return)%>%   pivot_longer(`2015`:`2016`, names_to = "year", values_to = "return")

##we lose info when the data frame is changed from wide to long
```
pivot_longer() has a names_ptypes argument, e.g.  names_ptypes = list(year = double()). What does it do?

change year format (chr) to dbl format

Why does this code fail?
```{r}
library(tidyverse)
table4a %>% 
  pivot_longer(c(1999, 2000), names_to = "year", values_to = "cases")

```
The values 1999 and 2000 are not in the data frame


What would happen if you widen this table? Why? How could you add a new column to uniquely identify each value?

```{r}
people <- tribble(
  ~name,             ~names,  ~values,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)

people %>%
  group_by(name, names) %>%
  mutate(obs = row_number()) %>%
   pivot_wider(names_from = "names", values_from = "values")
##works for now, but need to see if there is a reason in the data why 
##"Philip Woods is there 2x"

```
Exercises
What do the extra and fill arguments do in separate()?
Experiment with the various options for the following two toy datasets.

```{r}

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  print()

##separate into columns based on "one", "two", "three", would do based on commas

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>%   separate(x, into = c("one", "two", "three"),
  extra = "warn", fill = "warn") %>%
  print()

##extra = warn, means that if we have excess data that does not fit our columns, the system will return a warning. We could also drop or merge


##if I didn't want the warning

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>%   separate(x, into = c("one", "two", "three"),
  extra = "drop", fill = "warn") %>%
  print()


```

```{r}
##New tibble to test out fill argument

##fill = warn, means that it will return a warning if we there is not enough data pieces to fit our columns

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three")) %>%
  print()

##with fill
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), 
           fill = "warn") %>%
  print()
```

Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?

For separate(), remove = TRUE eliminates the input column in the resuting data frame. This would be useful if you only want the resulting columns

For unite(), remove = TRUE does the same thing as mentioned in separate().

Compare and contrast separate() and extract(). Why are there three variations of separation (by position, by separator, and with groups), but only one unite?

extract() takes groups (that you can set) and puts them in a new column, while separate() forms groups based on non-alpha separators in a column and puts the groups in new columns
Extract() has more options than seprate()

With unite() you are just combining columns so there is only one option for the columns you are combini