---
title: "Week 7 Summary"
output: html_notebook
---

Required Librarie
```{r}
library(tidyverse)
library(nycflights13)
library(maps)
```

13.4.6 Exercises
Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays. Here’s an easy way to draw a map of the United States:

```{r}
airports %>%
  semi_join(flights, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point() +
    coord_quickmap()1

```


Add the location of the origin and destination (i.e. the lat and lon) to flights.

```{r}
airport_locations <-airports %>%
  select(faa, lat, lon)

flights %>%
  select(year:day, hour, origin, dest) %>%
  left_join(airport_locations, c("origin" = "faa")) %>%
  left_join(airport_locations, c("dest" = "faa")) %>%
  print()
```


Is there a relationship between the age of a plane and its delays?

```{r}
airplaneage <- planes %>%
  select(tailnum, year)

airplanedelay <-flights %>%
  select(tailnum, dep_delay)

agedelay <-left_join(airplaneage, airplanedelay, by = "tailnum") %>%
  ggplot(aes(year, dep_delay), na.rm = TRUE) +
    geom_point()%>%
  print()

##better version

plane_cohorts <- inner_join(flights,
  select(planes, tailnum, plane_year = year),
  by = "tailnum"
) %>%
  mutate(age = year - plane_year) %>%
  filter(!is.na(age)) %>%
  mutate(age = if_else(age > 25, 25L, age)) %>%
  group_by(age) %>%
  summarise(
    dep_delay_mean = mean(dep_delay, na.rm = TRUE),
    dep_delay_sd = sd(dep_delay, na.rm = TRUE),
    arr_delay_mean = mean(arr_delay, na.rm = TRUE),
    arr_delay_sd = sd(arr_delay, na.rm = TRUE),
    n_arr_delay = sum(!is.na(arr_delay)),
    n_dep_delay = sum(!is.na(dep_delay))
  )
ggplot(plane_cohorts, aes(x = age, y = dep_delay_mean)) +
  geom_point() +
  scale_x_continuous("Age of plane (years)", breaks = seq(0, 30, by = 10)) +
  scale_y_continuous("Mean Departure Delay (minutes)")

```


What weather conditions make it more likely to see a delay?

```{r}
flight_weather <-
  flights %>%
  inner_join(weather, by = c(
    "origin" = "origin",
    "year" = "year",
    "month" = "month",
    "day" = "day",
    "hour" = "hour"
  ))

flight_weather %>%
  group_by(precip) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = precip, y = delay)) +
  geom_line() + geom_point() %>%
  print()

flight_weather %>%
  group_by(wind_gust) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = wind_gust, y = delay)) +
  geom_line() + geom_point() %>%
  print()

flight_weather %>%
  group_by(wind_speed) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = wind_speed, y = delay)) +
  geom_line() + geom_point() %>%
  print()

```


What happened on June 13 2013? Display the spatial pattern of delays, and then use Google to cross-reference with the weather.
```{r}
flights %>%
   filter(year == 2013, month == 6, day == 13) %>%
  group_by(dest) %>%
  summarise(delay = mean(arr_delay, na.rm = TRUE)) %>%
  inner_join(airports, by = c("dest" = "faa")) %>%
  ggplot(aes(y = lat, x = lon, size = delay, colour = delay)) +
  borders("state") +
  geom_point()  +
  coord_quickmap() 

##per google, time of the derechos
```
13.5.1 Exercises

What does it mean for a flight to have a missing tailnum? What do the tail numbers that don’t have a matching record in planes have in common? (Hint: one variable explains ~90% of the problems.)

```{r}

flights %>%
  anti_join(planes, by = "tailnum") %>%
  count(carrier, sort = TRUE) %>%
  mutate(p = n / sum(n))

```


Filter flights to only show flights with planes that have flown at least 100 flights.

```{r}
flights %>%
  count(tailnum, sort = TRUE, na.rm = TRUE)%>%
  filter(n > 99) %>%
  print()
```


Combine fueleconomy::vehicles and fueleconomy::common to find only the records for the most common models.

```{r}
library(fueleconomy)

vehicles %>%
  semi_join(common, by = c("make", "model")) %>%
  print()
```


What does anti_join(flights, airports, by = c("dest" = "faa")) tell you? What does anti_join(airports, flights, by = c("faa" = "dest")) tell you?



```{r}
test1 <-anti_join(flights, airports, by = c("dest" = "faa"))
print(test1)

```
```{r}
test2 <-anti_join(airports, flights, by = c("faa" = "dest"))
print(test2)
```
I'm guessing that there are different sources that the table data results from.

