---
title: "Week 11 Summary"
output: html_notebook
---

```{r}
library(tidyverse)
library(forcats)
```

15.4.1 Exercises
**There are some suspiciously high numbers in tvhours.**
**Is the mean a good summary?**

No, as the high numbers will sway the mean. Median might be a better summary

**For each factor in gss_cat,**
**identify whether the order of the levels is arbitrary or principled.**

```{r}
keep(gss_cat, is.factor)%>% names()
```
```{r}
print(paste("marital_levels"))
levels(gss_cat$marital)
print(paste("race_levels"))
levels(gss_cat$race)
print(paste("rincome_levels"))
levels(gss_cat$rincome)
print(paste("partyid_levels"))
levels(gss_cat$partyid)
print(paste("relig_levels"))
levels(gss_cat$relig)
print(paste("denom_levels"))
levels(gss_cat$denom)
```


**Why did moving “Not applicable” to the front of the levels**
**move it to the bottom of the plot?**
That would give it a value of 1

**How have the proportions of people identifying**
**as Democrat, Republican, and Independent changed over time?**

```{r}
gss_cat %>%
  mutate(
    partyid =
      fct_collapse(partyid,
        other = c("No answer", "Don't know", "Other party"),
        rep = c("Strong republican", "Not str republican"),
        ind = c("Ind,near rep", "Independent", "Ind,near dem"),
        dem = c("Not str democrat", "Strong democrat")
      )
  ) %>%
  count(year, partyid) %>%
  group_by(year) %>%
  mutate(p = n / sum(n)) %>%
  ggplot(aes(
    x = year, y = p,
    colour = fct_reorder2(partyid, year, p)
  )) +
  geom_point() +
  geom_line() +
  labs(colour = "Party ID.")
```


**How could you collapse rincome into a small set of categories?**

```{r}
gss_cat %>%
  mutate(rincome = fct_lump(rincome)) %>%
  count(rincome)
```

Not changing levels, so a new solution is:
```{r}
library("stringr")
gss_cat %>%
  mutate(
    rincome =
      fct_collapse(
        rincome,
        `Unknown` = c("No answer", "Don't know", "Refused", "Not applicable"),
        `Lt $5000` = c("Lt $1000", str_c(
          "$", c("1000", "3000", "4000"),
          " to ", c("2999", "3999", "4999")
        )),
        `$5000 to 10000` = str_c(
          "$", c("5000", "6000", "7000", "8000"),
          " to ", c("5999", "6999", "7999", "9999")
        )
      )
  ) %>%
count(rincome)

```
Pipes

```{r}
library(magrittr)
```
No exercises