---
title: "Week 8 Summary"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

14.2.5 **Exercises In code that doesn't use stringr, you'll often see
paste() and paste0(). What's the difference between the two functions?**

paste0 is faster

**What stringr function are they equivalent to? How do the functions
differ in their handling of NA?**

str_c() Differs in the default separator is an empty string, sep = "",
as opposed to a space, so it's more like paste0().

paste() turns missing values into the string "NA", whereas str_c()
propagates missing values. That means combining any strings with a
missing value will result in another missing value.

**In your own words, describe the difference between the sep and
collapse arguments to str_c().**

sep is the variable between vectors, while collapse is for combining.

**Use str_length() and str_sub() to extract the middle character from a
string. What will you do if the string has an even number of
characters?**

```{r}
library(stringr)
x <- c("Hello World")
str_length(x)

str_sub(x, -1, -6)
```

**What does str_wrap() do? When might you want to use it?**

Wraps word into paragraphs. Printing results

**What does str_trim() do? What's the opposite of str_trim()?**

Removes white space at the end of a string. str_pad() adds whitespace

**Write a function that turns (e.g.) a vector c("a", "b", "c") into the
string a, b, and c. Think carefully about what it should do if given a
vector of length 0, 1, or 2.**

```{r}
str_exp <- function(x, delim = ",") {
  n <- length(x)
  if (n == 0) {
    ""
  } else if (n == 1) {
    x
  } else if (n == 2) {
    # no comma before and when n == 2
    str_c(x[[1]], "and", x[[2]], sep = " ")
  } else {
    # commas after all n - 1 elements
    not_last <- str_c(x[seq_len(n - 1)], delim)
    # prepend "and" to the last element
    last <- str_c("and", x[[n]], sep = " ")
    # combine parts with spaces
    str_c(c(not_last, last), collapse = " ")
  }
}
x <- c("a", "b", "C")
str_exp(x)
```

**14.3.1.1 Exercises** **Explain why each of these strings don't match a
: "","\\","\\".**

: is for a colon "" is for space"\\" is a literal backslash "\\" is 2
literal backslashes

**How would you match the sequence "\...\..."?**

"\\...\\..."

**What patterns will the regular expression "\...\..." match? How would
you represent it as a string?** ......

"\\..\\..\\.."

**14.3.2.1 Exercises**

**How would you match the literal string "**$^$"?

"\$\^\$"

**Given the corpus of common words in stringr::words, create regular
expressions that find all words that:**

**Start with "y".**
```{r}
str_view(stringr::words, "^y", match = TRUE)
```


**End with "x"**

```{r}
str_view(stringr::words, "x$", match = TRUE)
```


**Are exactly three letters long.**

```{r}
str_view(stringr::words, "^...$", match = TRUE)
```

**Have seven letters or more.**

```{r}
str_view(stringr::words, "^.......", match = TRUE)
```